\documentclass{resume} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage[utf8]{inputenc}
\usepackage{helvet}
\usepackage{url}
\usepackage{pdfpages}

\setlength{\headerbuffer}{4pt}
\setlength{\secskip}{12pt}

\author{Troels Henriksen}
\email{athas@sigkill.dk}
\date{\today}

\renewcommand{\L}{$\mathcal{L}$}
\newcommand{\LO}{$\mathcal{L}_0$}

\begin{document}

\maketitle
\begin{center}
  \textbf{\today}
\end{center}
\section{Personal information}

\textbf{Citizenship:} Danish---
\textbf{Born:} 23rd of November, 1987---
\textbf{Languages:} Fluent in Danish and English

\section{Education}

Bachelors (2010), masters (2014), and PhD (2017) degrees in computer
science from DIKU, at the University of Copenhagen.

\section{Research Interests in Computing}

With references to representative publications.

\begin{itemize}
\item The \textbf{software-hardware boundary}, in particular mapping
  high-level language concepts efficiently onto \textbf{parallel and
    distributed systems} or
  accelerators. \cite{Henriksen:2017:FPF:3062341.3062354,Henriksen:2019:IFN:3293883.3295707,Larsen:2017:SRS:3122948.3122952,10.1145/2898354}
\item The combination of \textbf{high-performance computing} and
  \textbf{high-productivity computing}.~\cite{giesekemassively,lindh2019a,10.1145/3331553.3342617,Elsman:2019:DFE:3315454.3329955}
\item I am motivated by combining \textbf{theory, practice, and solid
    engineering}, to demonstrate ideas that \textit{actually work},
  rather than being fragile proofs of
  concepts.\cite{Henriksen:2017:FPF:3062341.3062354,Henriksen:2019:IFN:3293883.3295707,Elsman:2018:SIH:3243631.3236792,10.1007/978-3-030-18506-0_7}
\end{itemize}

As an applied researcher, I put significant effort into making my work
useful to others.  The Futhark language has been used for teaching and
projects at several universities (to my knowledge DIKU, Chalmers, and
HEPIA), as well as some ``real world'' usage.

\section{Academic and Work experience}

\begin{description}
\item[2009--2014]: TA in various DIKU courses ($16$ positions in
  total), in many cases participating in censor meetings.
\item[2014--2017]: PhD student at DIKU.
\item[2017--]: Post-doctoral researcher at DIKU.
\end{description}

Additionally:

\begin{description}
\item[March 2013--March 2014:] Student programmer/research assistant as
  part of the \L{} project at DIKU, developing the \LO{} language and
  compiler (now Futhark).
\item[July 2014:] Intern at Lawrence Livermore National Laboratory
  (LLNL), where I worked on a domain-specific language (DSL) embedded
  in C++ and generating CUDA code, for expressing problems in
  molecular dynamics.
\item[February 2017--March 2017:] Intern at the Danish company
  SimCorp, where I ported a Heston calibration program from OCaml to
  Futhark.
\end{description}

\section{Publication Summary}

I have authored and co-authored several articles in international
peer-reviewed conference proceedings and journals, including premiere
venues such as PLDI, TACO, ICFP, PPoPP, and ICDE.  The majority of my
work centres on studying optimising compilers for high-level
languages, in particular in conjunction with the Futhark
project.\footnote{\url{https://futhark-lang.org}} I have also
participated in collaborative works where my research was applied in
practice to computational problems in medical imaging and data
science.

\newpage

\section{Bibliography}

\nocite{*}
\bibliographystyle{these}
\bibliography{troelshenriksen}

\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
